An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-07-24 journal/poly-embed.tex
Added corollary that IE is sufficient

\begin{theorem}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.  Rinse and repeat for vertices of the expected loss on all possible (finite) supports.  As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?  Unclear on that gap.}
	\jessie{Cut everything but last paragraph}
	The first statement is a trivial corollary of Theorem~\ref{thm:poly-embeds-discrete}.
%	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
%	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
%	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
%	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
%	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
%	
%	Now let $\Gamma := \Gamma[L]$.
%	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
%	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
%	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
%	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
%	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
%	
%	Now consider $\Y'\subset \Y$.
%	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
%	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
%	
%	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
%	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
%	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}

@@

%\begin{definition}\label{def:indirectly-elicits}
%	A loss $L$ indirectly elicits a property $\Gamma:\simplex \toto \R$ if it elicits a property $\Gamma': \simplex \toto \R'$ such that there is a function $\psi:\R' \to \R$ such that for all $r \in \R'$, we have $\Gamma'_r \subseteq \Gamma_{\psi(r)}$.
%\end{definition}
%Note that $\Gamma$ embedding $\gamma$ implies $L$ indirectly elicits $\gamma$.

>>>>

\begin{theorem}\label{thm:ie-iff-embeds-refinement}
	Every polyhedral loss embeds a finite elicitable property.
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	\jessie{Intuition: There are only a finite set of possible vertices of the loss, and claim that for each $p \in \simplex$, one of these vertices is a minimizer of $\inprod{p}{L(\cdot)}$.  Rinse and repeat for vertices of the expected loss on all possible (finite) supports.  As there is a some vertex in the property value for every $p \in \simplex$, we have $\trim(\Gamma)$ finite, which yields the results via Prop 3 somehow?  Unclear on that gap.}
	\jessie{Cut everything but last paragraph}
	The first statement is a trivial corollary of Theorem~\ref{thm:poly-embeds-discrete}.
%	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
%	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
%	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
%	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
%	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
%	
%	Now let $\Gamma := \Gamma[L]$.
%	We claim for all $p\in\inter\simplex$, that $\Gamma(p) \cap V_\Y \neq \emptyset$.
%	To see this, let $u \in \Gamma(p)$, and $u' = (u,\inprod{p}{L(u)}) \in P(p)$.
%	The optimality of $u$ is equivalent to $u$ being contained in the face exposed by the normal $(0,\ldots,0,-1)\in\reals^{d+1}$, which is a face of $P(p)$.
%	Let $v'\in\reals^{d+1}$ be a vertex on such a face, and $v\in V_\Y$ its projection onto $\reals^d$.
%	Then $v$ is also optimal, and therefore $v\in\Gamma(p)$.
%	
%	Now consider $\Y'\subset \Y$.
%	Applying the above argument on distributions $p$ with support exactly $\Y'$, we have a similar guarantee: a finite set $V_{\Y'}$ such that $\Gamma(p) \cap V_{\Y'} \neq \emptyset$ for all $p$ with support exactly $\Y'$.
%	(When $\Y' = \{y\}$ is a singleton, we simply take the projected vertices of $L(\cdot)_y$.)
%	
%	Thus, taking $V = \bigcup_{\Y'\subseteq\Y} V_{\Y'}$, we have for all $p\in\simplex$ that $\Gamma(p) \cap V \neq \emptyset$.
%	This implies that $\trim(\Gamma) \subseteq \{\Gamma_v : v\in V\}$, which is finite, so Proposition~\ref{prop:embed-trim} \jessie{also Prop 3} now gives the conclusion.
%	\jessiet{Do we need to show the preimage of $\Gamma$ is $V$?}

@@

\begin{corollary}\label{cor:ie-sufficient} \jessiet{Added 7.24.20.  Probably too long to be a Corollary proof, but would rather start too long than too short.  Also the proof has a forward ref}
	If a polyhedral loss $L:\reals^d \to \reals^\Y$ indirectly elicits a property $\gamma': \simplex \toto \R'$, then $L$ is calibrated with respect to any loss $\ell'$ eliciting $\gamma'$.
\end{corollary}
\begin{proof}
	By Theorem~\ref{thm:ie-iff-embeds-refinement}, we know that $\Gamma := \prop{L}$ embeds a property $\gamma\simplex \toto \R$ which refines $\gamma'$.
	Therefore, these exists a calibrated link $\psi : \reals^d \to \R$ from $\Gamma$ to $\gamma$.
	Moreover, as $\gamma$ refines $\gamma'$, take any link $\psi': r \mapsto r'$, where $\gamma_r \subseteq \gamma'_{r'}$. 
	(We know such a link exists by refinement.)
	Consider $\tilde \psi := \psi \circ \psi'$.

	Now, we show that $(L, \tilde \psi)$ is calibrated with respect to $\ell'$.
	Consider that since $\Gamma$ embeds $\gamma$, we have a link $\bar \psi$ such that $(L,\bar \psi)$ is calibrated with respect to $\ell$ eliciting $\gamma$.
	It then suffices to show
	\begin{align*}
	\inf_{u}\inprod{p}{L(u)} &< \inf_{u : \psi(u) \not \in \gamma(p)} \inprod{p}{L(u)}\\
	&\leq \inf_{u : \psi'(u) \not \in \gamma'(p)} \inprod{p}{L(u)}~.~
	\end{align*}
	This first statement is true as embedding implies calibration (Theorem~\ref{thm:eps-thick-calibrated}), and the second is true if $\{u : \psi'(u) \not \in \gamma'(p) \} \subseteq \{u : \psi(u) \not \in \gamma(p) \}$; we show the contrapositive.
	Take $u \in \reals^d$ so that $\psi(u) \in \gamma(p)$.
	\begin{align*}
	\psi(u) \in \gamma(p) &\iff \psi' \circ \psi(u) \in \psi' \circ \gamma(p)\\
	&\iff \tilde \psi(u) \in \gamma'(p)~,~
	\end{align*}
	where the last inequality follows by construction of $\psi'$.
\end{proof}
